Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-03-28 WSSSPE1_report/WSSSPE1_summary_report.tex
small change

% Why are we classifying software like above?
This classification is motivated by our argument that the software projects
wildly vary in factors such as scope, purpose and usage. The development and
management of software is significantly influenced by these factors.
Consequently, the sustainability challenges faced by software differ and must
be treated separately. For instance, the challenges faced by a gateway software
development project such as \textit{CIPRES} are distinct to a niche software
for ab initio modeling and simulation such as \textit{VASP}.

>>>>

% Why are we classifying software like above?
This classification is motivated by our argument that the software projects
wildly vary in factors such as scope, purpose and usage. The development and
management of software is significantly influenced by these factors.
Consequently, the sustainability challenges faced by software differ and must
be treated separately. For instance, the challenges faced by a gateway software
development project such as \textit{CIPRES} or \textit{VisIT} are distinct to a
niche software for ab initio modeling and simulation such as \textit{VASP} or
\textit{Quantum Espresso}.
